%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Bharat}{Sahni}{ \urlstyle{same}\
\href{mailto:sahni.bharat05@gmail.com}{sahni.bharat05@gmail.com} | +91 9807873746 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Jaypee Institute of Information Technology}
\descript{BTech in Computer Science}
\location{July 2018 | Noida}
\location{Cum. GPA: 7.3/10}
\sectionsep

\subsection{XII(Senior Secondary)}
\location{Year of Completion:2014}
\location{ISC Board | Lucknow Public College}
\location{Percentage : 93.5}
\sectionsep

\subsection{X(Secondary)}
\location{Year of Completion:2012}
\location{ICSE Board | Lucknow Public College}
\location{Percentage : 89.4}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://facebook.com/sahnibharatt}{\bf sahnibharatt} \\
Github:// \href{https://github.com/sahnibharat}{\bf sahnibharat} \\
LinkedIn://  \href{https://www.linkedin.com/in/sahnibharat}{\bf sahnibharat} \\
Hackerrank://  \href{https://www.hackerrank.com/provethemwrong}{\bf provethemwrong}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     POSITION OF RESPONSIBILITY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Positions Of Responsibility}
\textbullet{} Campus Ambassador for GeeksForGeeks\\
\textbullet{} Core Team member at Panache\\
\textbullet{} Core Team member at Connecting Dreams Foundation\\
\textbullet{} Event Manager(Poise) at Converge 2016\\
\textbullet{} Event Manager(Poise) at Converge 2017\\
\textbullet{} Informal Event Head at Converge 2017\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Experienced:}
Java \textbullet{}   AWS \textbullet{} ASP.NET MVC\textbullet{} Cloud Computing \textbullet{}
Django \textbullet{} BootStrap \textbullet{} CSS \\ 
C \textbullet{} C++ \textbullet{} CSharp \textbullet{}  MySQL\\
\location{Familiar:}
Python \textbullet{} Android \textbullet{} MachineLearning \textbullet{} PHP  \textbullet{} Oracle
 \textbullet{} Spring Hibernate
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Newgen Softwares}
\descript{| Software Engineer +Software Engineer Intern }
\location{February 2018 - Present | Noida, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Software Developer Intern till July 2018.
\item Worked in Cheque Truncation Group of the Organization. 
\item Developed modules for Bank Of Baroda, Deutsche Bank, Bank of America.
\end{tightemize}
\sectionsep

\runsubsection{Tata Consultancy Services}
\descript{| Summer Intern }
\location{June 2017 – July 2017 | Lucknow, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item 8 out of 100 applicants chosen to be a Summer Intern 2017 at Lucknow.
\item Developed Cloud based Web Application on AWS using PHP, MySQL, JavaScript, Bootstrap, CSS
\end{tightemize}
\sectionsep

\runsubsection{5thDimension Studio}
\descript{| Web Developer Intern }
\location{Jan 2017 – March 2017 | Delhi, India}
\begin{tightemize}
\item Developed their website from the ground up.
\item Developed using PHP, AJAX, Bootstrap, CSS, JavaScript, JQuery.
\item Visit \href{http://5thdimension.studio/}{\bf http://5thdimension.studio/} 
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Moodle Quiz}\\
Desktop application that uses socket programming to conduct Quiz in a local
network. Technology used was J2EE, JDBC, Socket Programming.
\runsubsection{Find My Medicines}\\
AWS hosted web app that search for medicines and tell you the nearest Medical Shop with its availability. Technology used were PHP, Bootstrap, MySQL,
AWS.\\
\runsubsection{Twitter Personality Analysis}\\
Web application to analyse Twitter profile using self designed algorithm. Django Framework was used to develop this project.\\
\runsubsection{Service Controller}\\
Bank of Baroda web utility to start, stop and restart windows services
remotely from a machine in a shared network. Technology used was DotNet MVC, Razor
and Oracle database.\\
\runsubsection{BOB Search Utility}\\
Web app to search for cheques in Cheque Truncation System. Technology used is DotNet MVC, Oracle database and Razor.\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
\begin{tabular}{rll}
2017	     & Won Bronze medal at Hackerrank's Week of Code 33\\
2017	     & 5 Star Profile in Problem Solving at Hackerrank\\
2017	     & 4 Star Profile in Java at Hackerrank\\
2017	     & Won Second Prize in Converge 2017 Weightlifting Competition\\
2017	     & Successfully administered JIIT Youth Marathon\\
2017	     & Successfully administered Poise Fashion Event\\
2017	     & Successfully administered Freshers Event\\
2016	     & Came 4th in JIIT Youth Marathon\\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications} 
\textbullet{} \href{https://www.geeksforgeeks.org/arraylist-in-java/}{\bf https://www.geeksforgeeks.org/arraylist-in-java/}


\end{minipage} 
\end{document}  \documentclass[]{article}
